---
title: "Eating Out"
author: "Teresa Juan"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data comes from the 1996 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```


In the percentile data we can see that white group go out to eat more then black group, and the white people go out to eat more than the other group. However looking at th black group and the others there isn’t  much of a difference. So this makes us wonder why do the white people go out to eat more then the other two groups?. In the frequency chart we see that we have about 1000 white guys and about 250 black guys and 150 other that did this survey. This might be a reason why the white group had a higher percentage in eating out because there were more of them doing the survey.


```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

In the first table date we see there an 83% of white people that do eat out more out of 100%, black eat out 70% more out of 100% and others eat out 73% more out of 100%. It seems to me that there isn't much of a difference between others and the black eating out but it its clear that the white eat out more than these two groups.


